Icicle: a single-pass query language

### 2015-11-14 2016icicle/Main.tex
Icicle paper

% Note:
% install dot2tex with
% $ pip install dot2tex
% $ mkdir out
% then compile with shell escape enabled:
% $ latexmk --view=pdf --latexoption="-shell-escape"

@@

% for combinator pictures
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage[outputdir={out/}]{dot2texi}

@@

\title{Merging merges, more or less}

\authorinfo{
  Amos Robinson$^\dagger$ 
  \and Ben Lippmeier$^\dagger$
  \and Gabriele Keller$^\dagger$ 
  \and Manuel Chakravarty$^\dagger$ 
}{
  \vspace{5pt}
  \shortstack{
    $^\dagger$Computer Science and Engineering \\
    University of New South Wales, Australia \\[2pt]
    \textsf{\{amosr,benl,keller,chak\}@cse.unsw.edu.au}
  }
}

@@

\begin{abstract}
Fusion is an essential part of optimising high-level array computations.
Fusion systems for combinators tend to focus on combinators with data-independent access patterns such as @zip@, @filter@ and @map@, while ignoring @merge@ as in merge sort.
In this paper, we show that describing combinators as deterministic finite automata allows us to express more combinators, while leading to a fusion algorithm based on intersection of automata.
\end{abstract}

@@

\keywords
	Arrays; Fusion; Haskell

\input{section/01-Introduction.tex}
\input{section/02-Machines.tex}
\input{section/03-Merging.tex}
\input{section/04-Invariants.tex}
\input{section/05-Proofs.tex}
\input{section/06-Conclusion.tex}
% \input{section/XX-RelatedWork.tex}

\section*{Acknowledgements}
The audience of the inaugural SAWDAP workshop, especially Thomas Sutton and Patryk Zadarnowski, were very helpful in an early version of this work.

>>>>

@@

@@

\title{Icicle: a single-pass query language}

\authorinfo{
  Amos Robinson$^\dagger$$^\ddagger$
  \and Huw Campbell$^\ddagger$
  \and Mark Hibberd$^\ddagger$
  \and Tran Ma$^\ddagger$
  \and Jacob Stanley$^\ddagger$
}{
  \vspace{5pt}
  \shortstack{
    $^\dagger$Computer Science and Engineering \\
    University of New South Wales, Australia \\[2pt]
    \textsf{amosr@cse.unsw.edu.au}
  }
  \shortstack{
    $^\ddagger$Ambiata      \\
    Big data and shit       \\[2pt]
    \textsf{\{first.last\}@ambiata.com}
  }
}

@@

\begin{abstract}
When streaming a large amount of data, simply iterating over the data may take hours.
In this case, the difference between a query that takes one iteration and a query that takes multiple iterations must be very explicit.
For many purposes, limiting queries to a single pass is sufficient.
We introduce a type system based on modality types to enforce this single pass restriction.
By using an appropriate intermediate language we can fuse multiple independent queries together, before extracting efficient single-loop C code.
\end{abstract}

@@

\keywords
	Arrays; Fusion

\input{section/01-Introduction.tex}
\input{section/02-Source.tex}
\input{section/03-Types.tex}

\section*{Acknowledgements}
I would like to thank all of Ambiata for allowing me to work on such an interesting and useful problem, and on top of that being the most sensible group of people I have ever had the pleasure of working with.
